Hidden network-size assumptions\\in the maximum-entropy method

### 2017-05-04 maxNt.tex
update luca's bib

This simple example shows that the multiplicity inspection that must
precede a \me\ application already involve probability considerations at
the level of the full network. The usual reasoning by enumeration
implicitly assumes a uniform distribution, or a ***

We:
\begin{enumerate}
\item have a network with $\yN$ units, $2^{\yN}$ possible states
\item expect averages of $\yxs$ active neurons and $\yxxs$ active pairs
\item use maximum-entropy to choose a probability distribution for the
  states of the $\yN$ units conforming to our expectations.
\end{enumerate}

>>>>

This simple example shows that the multiplicity inspection that must
precede a \me\ application already involves probability considerations at
the level of the full network. The usual reasoning by enumeration
implicitly assumes a uniform distribution or at least a \emph{factorizable}
distribution.

***If the distribution is factorizable, however, it means that examination of
the subnetwork \emph{cannot give us any insights about the network it is a
  part of}. This is obviously contrary to the reason why we made neuronal observations.

Consider the following ways of proceeding. We:
\begin{enumerate}
\item have a network with $\yN$ units, $2^{\yN}$ possible states
\item expect averages of $\yxs$ active neurons and $\yxxs$ active pairs
\item use maximum-entropy to choose a probability distribution for the
  states of the $\yN$ units conforming to our expectations.
\end{enumerate}
